### 2016-01-18 docs/ms_communitySynchrony.Rmd
small changes to title page

\textit{Authorship}: ATT, CdM, and PBA designed the research, ATT performed the research, and ATT, CdM, ML, and PBA contributed to the analyses and interpretation of results. All authors contributed to writing the manuscript.

@@

\textit{Running Title}: Species synchrony in grasslands

\textit{Article Type}: Letter

\textit{Number of Words}: Abstract = ; Main Text =

\textit{Number of References}:

\textit{Number of Tables and Figures}:  Tables;  Figures

\textit{Corresponding Author}: Andrew Tredennick \\  
Address: Department of Wildland Resources and the Ecology Center, 5230 Old Main Hill, Utah State University, Logan, Utah 84322 USA \\
Phone: +1-970-443-1599 \\
Fax: +1-435-797-3796 \\
Email: atredenn@gmail.com

@@

What temporal variable should we use to measure synchrony?
In constrast to virtually every study on synchrony that uses population abundance (CITATIONS), @Loreau2008a suggest community-wide synchrony is best viewed through the lense of per capita growth rates.
On conceptual grounds, per capita growth rates represent the immediate response of species to the environment and competition that we wish to attribute to synchrony.
On practical grounds, positively covarying abundances and negatively covarying environmental responses are not mutually exclusive [@Loreau2008a].
Therefore, measuring the synchrony of population abundances through time does not allow inference on the drivers of synchrony.

Aside from issues on how to measure synchrony, disentangling the factors that drive species syncrony is difficult.
Observational timeseries of species' abundances allows easy quantification of summed covariances [@Houlahan2007] or species synchrony [@Gross2014], but quantifying the relative influence of density-dependence, demographic stochasticity, and environmental stochasticity remains a challenge.
Indeed, to our knowledge, only one study has attempted to separate the influences of density-dependence and environmental stochasticity directly [@Mutshinda2009].
@Mutshinda2009 used a statistical technique to decompose synchrony of species' abundances calculate from five time series.
They found that the effect of environmental forcing on temporal dynamics is much stronger than that of interspecific interactions, across all taxa they analyzed [@Mutshinda2009].
However, the @Mutshinda2009 study did not include data from plant communities that have, so far, received the most evidence for a strong role for interspecific interactions in driving species asynchrony [@Gross2014].

>>>>

\vspace{2em}

@@

\vspace{2em}

\textbf{Authorship}: ATT, CdM, and PBA designed the research, ATT performed the research, and ATT, CdM, ML, and PBA contributed to the analyses and interpretation of results. All authors contributed to writing the manuscript.

\textbf{Running Title}: Drivers of species synchrony in natural grasslands

\textbf{Article Type}: Letter

\textbf{Number of Words}: Abstract = ; Main Text =

\textbf{Number of References}:

\textbf{Number of Tables and Figures}:  Tables;  Figures

\textbf{Corresponding Author}: Andrew Tredennick \\  
Address: Department of Wildland Resources and the Ecology Center, 5230 Old Main Hill, Utah State University, Logan, Utah 84322 USA \\
Phone: +1-970-443-1599 \\
Fax: +1-435-797-3796 \\
Email: atredenn@gmail.com

@@

What temporal variable should we use to measure synchrony?
In constrast to virtually every study on synchrony that uses population abundance [e.g., @Houlahan2007; @Mutshinda2009; @Hector2010; @Gross2014; @Vasseur2014], @Loreau2008a suggest community-wide synchrony is best viewed through the lense of per capita growth rates.
On conceptual grounds, per capita growth rates represent the immediate response of species to the environment and competition that we wish to attribute to synchrony.
On practical grounds, positively covarying abundances and negatively covarying environmental responses are not mutually exclusive [@Loreau2008a; @Ranta2008].
Therefore, measuring the synchrony of population abundances through time does not allow inference on the drivers of synchrony.

Aside from issues on how to measure synchrony, disentangling the factors that drive species syncrony is difficult.
Observational timeseries of species' abundances allows easy quantification of summed covariances [@Houlahan2007] or species synchrony [@Gross2014], but quantifying the relative influence of density-dependence, demographic stochasticity, and environmental stochasticity remains a challenge.
Indeed, to our knowledge, only one study has attempted to separate the influences of density-dependence and environmental stochasticity directly [@Mutshinda2009].
@Mutshinda2009 used a statistical technique to decompose synchrony of species' abundances calculate from five time series.
They found that the effect of environmental forcing on temporal dynamics is much stronger than that of interspecific interactions, across all taxa they analyzed [@Mutshinda2009].
However, the @Mutshinda2009 study did not include data from plant communities that have, so far, received the most evidence for a strong role for interspecific interactions in determining species synchrony [@Gross2014].
